\item W.C. Shiu, X.G. Chen and W.H. Chan, Triangle-free
graphs with large independent domination number, {\it
Discrete Opt.}, {\bf 7}, 86-92 (2010).

\item W.C. Shiu, X. Chen and W.H. Chan, Uniformly pair-bonded
trees, {\it Ars Combin.}, {\bf 94} (2010), 71-78.

\item J. Li, W.C. Shiu and A. Chang, The number of spanning trees
of a graph, {\it Applied Math. Letters}, {\bf 23}, 286-290
(2010).

\item H. Zhang, D. Ye and W.C. Shiu, Forcing matching
number of fullerence graphs, {\it Appl. Discrete Math.},
{\bf 158}, 573-582 (2010).

\item J. Li, W.C. Shiu and A. Chang, On the $k$-th Laplacian
Eigenvalues of Trees with Perfect Matchings, {\it Linear
Algebra Appl.}, {\bf 432}, 1036-1041 (2010).

\item X. Chen and W.C. Shiu, A note on the domination
dot-critical graphs, {\it Discrete Appl. Math.}, {\bf 157},
3743-3745 (2009).

\item W.H. Chan, P.C.B. Lam and W.C. Shiu, Edge-face
total chromatic number of Halin graphs, {\it SIAM J.
Discrete Math.} {\bf 23}, 1646-1654 (2009).

\item D. Kremer and W.C. Shiu, Finite transition matrices for permutations
avoiding pairs of length four patterns, {\it Discrete
Math.}, {\bf 268}, 171-183 (2003).

\item P.C.B Lam, G. Liu, G. Li and W.C. Shiu, Orthogonal $(g,f)$-factorization
in networks, {\it Network}, {\bf 35 (4)}, 274-278 (2000).

\item P.C.B. Lam, W.C. Shiu, W.H. Chan and Y.X. Lin, On the bandwidth of convex
triangulation meshes, {\it Discrete Math.}, {\bf 173},
285-289 (1997).

\item W.C. Shiu, S.L. Ma and K.T. Fang, On the rank of cyclic Latin squares,
{\it Linear and Multilinear Algebra}, {\bf 40}, 183-188
(1995).

************************
\item J. Li, W.C. Shiu and A. Chang, On the Laplacian Estrada index of a
graph, {\it Application Analysis and Discrete Math.}, {\bf
3}, 147-156 (2009).

\item W.C. Shiu and R.M. Low, $\mathbb Z_k$-magic labelings of fans and
wheels with magic-value zero, {\it Australas. J. Combin.},
{\bf 45}, 309-316 (2009).

\item W.C. Shiu and H. Kwong, An algebraic approach for finding
balance index sets, {\it Australas. J. Combin.}, {\bf 45},
139-155 (2009).

\item W.C. Shiu, Correction to algebraic structure of Schur rings, {\it Chinese
Journal of Mathematics (R.O.C.)}, {\bf 23}, 193-194 (1995).
\item W.C. Shiu, Algebraic structure of Schur rings, {\it Chinese Journal of
Mathematics (R.O.C.)}, {\bf 21}, 55-71 (1993).

\item W.C. Shiu, Schur rings over dihedral groups, {\it Chinese Journal of
Mathematics (R.O.C.)}, {\bf 18}, 209-223 (1990).
