\documentclass{twarticle}
%\documentclass{article}
\textwidth=500pt
\textheight=675pt
\oddsidemargin=-0.3in \topmargin=-0.6in
\renewcommand{\baselinestretch}{1}
\renewcommand{\arraystretch}{1}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{CJK}
\usepackage{hyperref}
\usepackage{enumerate}%for enumerate environment
\hypersetup{backref,colorlinks=true,urlcolor=blue}
\begin{document}

\section{Books and Articles}
%\begin{CJK*}{Bg5}{song}
\begin{enumerate}[{[}1{]}]
\item W.C. Shiu, {\it Linear Algebra}, Department of Mathematics, Hong Kong Baptist
University, 2016.
\item W.C. Shiu and P.K. Sun, {\it A First Course in Graph
Theory}, Department of Mathematics, Hong Kong Baptist
University, 2014.
\item W.C. Shiu and L. Ling, {\it Smart Decisions},
Pearson, 2012.
\item W.C. Shiu and C.I. Chu, {\it Linear Algebra}, McGraw Hill, 2nd Ed. updated, 2012.
\item 邵慰慈、鄧文禮，{\it 統計學概論}，香港教育圖書公司，2008。
\item 潘建強、邵慰慈，{\it 基礎數論}， 勤達出版社，2008。
\item 邵慰慈，可支援中文的數學編輯軟件 -- PUTex，{\it DATUM（數學教育期刊）}，{\bf 42}，29-31
(2005)。
\item 唐創時、邵慰慈： 費馬最後定理的影響，{\it
文匯報}, Aug. 15, 2005。
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/fermat.pdf}{原文}
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/fermat_news.pdf}{新聞稿}
\item 邵慰慈、潘建強，{\it 基礎離散數學}， 九章出版社，2005。


\item 李華剛、廖俊傑、邵慰慈 ，{\it 統計學入門}，香港教育圖書公司，1997, 1999。

\item C.I. Chu and W.C. Shiu, {\it Lecture Notes on Linear Algebra}, Department of Mathematics, Hong Kong Baptist
University, 1994, 2nd edition 1996, 3rd edition
1998, 4th edition 2001.

\item W.C. Shiu, {\it Lecture Notes on Discrete Mathematics -- Graph Theory}, Department of Mathematics, Hong Kong Baptist
College, 1989.
\end{enumerate}
%\end{CJK*}
\section{224 published or accepted papers}

\begin{enumerate}[{[}1{]}]
\item Z.-B. Gao, W.C. Shiu, S-M. Lee, F. Wang and G-Y. Sun, Full edge-friendly index sets of one point union of cycles,
to appear in {\it ARS Combin.}, (2021) (accepted at Dec. 4, 2018).

\item G.C. Lau, W.C. Shiu and H.K. Ng, On local antimagic chromatic number of cycle-related join graphs, to appear in {\it Discussiones
Mathematicae Graph Theory}, accepted at Aug. 4, 2018.
    ArXiv: http://arxiv.org/abs/1805.04888

\item S. Wei and W.C. Shiu, Enumeration of Wiener indices in random polygonal chains, {\it J. Math. Anal. Appl.}, {\bf 469}, 537-548 (2019).

\item Q. Li, W.C. Shiu, P.K. Sun and D. Ye, On the anti-Kelul\'e problem of cubic graphs, {\it The Art of Discrete and Applied Mathematics}, {\bf 2}, \#P1.05, (2019).


\item J. Huo, W.C. Shiu and W-F. Wang, The neighbor expanded sum distinguishing index of Halin graphs, {\it Ars Combin.}, {\bf 141}, 63-73 (2018).

\item S. Wei and W.C. Shiu, The number of perfect matching in random polyazulenoid chains, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, {\bf 105}, 21-33 (2018).

\item J-M. Guo, Z-W. Wang, J. Li, W.C. Shiu and P-P. Tong, Corrigendum to ``The effect on eigenvalues of connected graphs by adding edges" [Linear Algebra
Appl. 548 (2018) 57-65], {\it Linear Algebra Appl.}, {\bf 555}, 434-436 (2018).

\item W.C. Shiu, Integer-antimagic spectra of disjoint unions of cycles, {\it Theory and Appl. of Graphs}, {\bf 5:Iss. 2}, Article 3, (2018).

\item J-M. Guo, P-P. Tong, J. Li, W.C. Shiu and Z-W. Wang, The effect on eigenvalues of connected graphs by adding edges, {\it Lin. Alg. Appl.}, {\bf 548}, 57-65 (2018).

\item G.C. Lau and W.C. Shiu, On SD-prime Labeling of Graphs, {\it Utilitas Mathematica}, {\bf 106}, 149-164 (2018).

\item Y. Wang, W.C. Shiu, W-F. Wang and M. Chen, Plane graphs with maximum degree $4$ are strongly $19$-edge-colorable, {\it Discrete Mathematics}, {\bf 341}, 1629-1635 (2018).

\item J. Li, J-M. Guo, W.C. Shiu, \c{S}.B.B. Altinda\u{g} and D. Bozkurt, Bounding the sum of powers of normalized Laplacian eigenvalues of a graph, {\it Applied Mathematics and Computation}, {\bf 324}, 82-92 (2018).

\item W.C. Shiu and R.M. Low, The Integer-magic spectra and null sets of the Cartesian product of two trees, {\it Australas. J. Combin.}, {\bf 70}, 157-167 (2018).

\item W.C. Shiu, Integer-antimagic spectra of fan, wheel and gear graphs, {\it J. Combin. Number Theory}, {\bf 9}, 229-238 (2017).

\item W.C. Shiu, G.C. Lau and S-M. Lee, On (Semi-)edge-primality graphs, {\it Iranian J. Mathematical Sciences and Informatics}, {\bf 12(1)}, 1-14 (2017).

\item J-M. Guo, J. Li, P. Huang and W.C. Shiu, Coefficients of the characteristic polynomial of the (signless, normalized) Laplacian of a graph, {\it Graphs and Combin.}, {\bf 33}, 1155-1164 (2017).

\item P. Huang, W.C. Shiu and P.K. Sun, A relationship between the walks and the semi-edge walks of graphs, {\it J. Math. Research Appl.}, {\bf 37}, 520-526 (2017).

\item Q. Wu and W.C. Shiu, Circular $L(j,k)$-labeling numbers of square paths, {\it J. Combin. Number Theory}, {\bf 9}, 41-46 (2017).

\item Q. Wu and W.C. Shiu, $L(j,k)$-labeling numbers of square of paths, {\it AKCE International J. Graphs Combin.}, {\bf 14}, 307-316 (2017).

\item J. Li and W.C. Shiu, Unicyclic graphs with a perfect matching having signless Laplacian eigenvalue two, {\it J. Math. Research Appl.}, {\bf 37}, 379-390 (2017).

\item W.C. Shiu, Full edge-friendly index sets of complete bipartite graphs,
{\it Trans. Combin.}, {\bf 6(2)}, 7-17 (2017).

\item W.C. Shiu, P. Huang, P.K. Sun, The signless Laplacian spectral radius of
$k$-connected irregular graphs, {\it Linear and Multilinear Algebra}, {\bf 65}, 830-839 (2017).

\item J. Li, J-M. Guo and W.C. Shiu, The minimum algebraic connectivity of graphs with a given
clique number, {\it Acta Math. Appl. Sinica}, (Chinese version), {\bf 39}, 928-937 (2016). (English
version: \href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p1170-final.pdf}{PDF1170})

\item D. Chen, W.C. Shiu, Q. Shu, P.K. Sun and W-F. Wang, A characterization of $L(2,1)$-labeling
number for trees with maximum degree $3$, {\it Acta Math. Sinca}, (Chinese version), {\bf 59},
685-710 (2016). (English version:
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p1510-final.pdf}{PDF1510})

\item G.C. Lau, W.C. Shiu, H.K. Ng, G.D. Ng and P. Jeyanthi, Further results on SD-prime labeling, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, {\bf 98}, 151-170 (2016).

\item G.C. Lau, W.C. Shiu and H.K. Ng, Further Results On Super Graceful Labeling of Graphs, {\it AKCE International Journal of Graphs and Combinatorics}, {\bf 13}, 200-209 (2016).

\item J-M. Guo, J. Li and W.C. Shiu, Effects on the normalized Laplacian spectral radius of non-bipartite graphs under perturbation and their applications, {\it Linear and Multilinear Algebra}, {\bf 64}, 2177-2187 (2016).

\item X. Hu, W-F. Wang, W.C. Shiu and Y. Wang, Plane graphs with maximum degree $9$ are entirely $11$-choosable, {\it Discrete Math.}, {\bf 339}, 2742-2753 (2016).

\item J. Li, Y. Liu and W.C. Shiu, The irregularity of two types of trees, {\it Discrete
Mathematics and Theoretical Computer Science}, {\bf 17(3)}, 203-216 (2016).

\item J-M. Guo, J. Li and W.C. Shiu, The largest normalized Laplacian spectral radius of
non-bipartite graphs, {\it Bull. Malays. Math. Sci. Soc.}, {\bf 39}, S77-S87 (2016).
DOI:10.1007/s40840-015-0241-y.

\item W.C. Shiu and R.M. Low, The integer-antimagic spectra of dumbbell graphs, {\it Bull. of ICA},
{\bf 77}, 89-110 (2016).

\item W.C. Shiu and R.M. Low, Integer-antimagic spectra of complete bipartite graphs and complete
bipartite graphs with a deleted edge, {\it Bull. ICA}, {\bf 76}, 54-68 (2016).

\item  W.C. Shiu, Extreme edge-friendly indices of complete bipartite graphs, {\it Trans. Combin.}, {\bf 5(3)}, 11-21 (2016).


\item Q. Wu, W.C. Shiu and P.K. Sun, $L(j,k)$-labeling number of Cartesian product of path and cycle, {\it J. Combin. Optim.}, {\bf 31}, 604-634 (2016). DOI:
10.1007/s10878-014-9775-4.

\item P. Huang, W.C. Shiu and P.K. Sun, Maximizing the spectral radius of $k$-connected graphs with given diameter, {\it Lin. Alg. Appl.}, {\bf 488}, 350-362 (2016).

\item W.C. Shiu, P.K. Sun and R.M. Low, The integer-antimagic spectra of tadpole and lollipop graphs, {\it Congr. Numer.}, {\bf 225}, 5-22 (2015).

\item  W.C. Shiu and G.C. Lau, Some results on $k$-edge-magic broken wheel graphs,
{\it J. Graph Labeling}, {\bf 1}, 65-79 (2015).

\item  W.C. Shiu, P.C.B. Lam and S-M. Lee, Edge-magic index sets
of square of paths, {\it Utilitas Mathematica}, {\bf 97}, 271-286 (2015).

\item Q. Li, W.C. Shiu and H. Yao, Matching
preclusion for cube-connected cycles, {\it Discrete Applied Math.}, {\bf 190-191}, 118-126 (2015).

\item J. Li, J-M. Guo, W.C. Shiu, A note on
Randi\'c energy, {\it MATCH Communications in Mathematical
and Computer Chemistry}, {\bf 74}, 389-398 (2015).

\item D.
Chen, W.C. Shiu, Q. Shu, P.K. Sun and W-F. Wang,
$(2,1)$-Total labeling of trees with large maximum degree,
{\it Discrete Appl. Math.}, {\bf 187}, 61-69 (2015).

\item
R. Liu and W.C. Shiu, General Randi{\'c} matrix and general
Randi{\'c} incidence matrix, {\it Discrete Applied Math.},
{\bf 186}, 168-175 (2015).

\item R. Liu, W.C. Shiu and J.
Xue, Sufficient spectral conditions on Hamiltonian and
traceable graphs, {\it Linear Alg. Appl.}, {\bf 467},
254-266 (2015).

\item H. Zhou, W.C. Shiu and P.C.B. Lam, Bounds on
$L(2,1)$-choice number of Cartesian products of paths
and spiders, {\it J. Combin. Number Theory}, {\bf
6(4)}, 219-231 (2014).

\item J. Li, J-M. Guo and W.C. Shiu, Bounds on normalized
Laplacian eigenvalues of graphs, {\it J. Inequalities and
Applications}, {\bf 2014:316} (2014). DOI:
10.1186/1029-242X-2014-316.

\item J. Li and W.C. Shiu, The
harmonic index of a graph, {\it Rocky Mountain J. Math.},
{\bf 44(5)}, 1607-1620 (2014).

\item J. Li and W.C. Shiu,
The spectral radii of graphs with prescribed degree
sequence, {\it Kyungpook Math. J.}, {\bf 54}, 425-441
(2014).

\item H. Zhou, W.C. Shiu and P.C.B. Lam, Notes on $L(1,1)$ and $L(2,1)$ labelings for $n$-cube,
{\it J. Combin. Optimization}, {\bf 28}, 626-638 (2014).

\item J-B. Lv, J. Li and W.C. Shiu, The harmonic index of
unicyclic graphs with given matching number, {\it
Kragujevac J. Math.}, {\bf 38}, 173-183 (2014).

\item J. Li and W.C. Shiu, The number of spanning trees of composite graphs,
{\it Journal of Combinatorial Mathematics and Combinatorial Computing}, {\bf 89}, 45-52 (2014).

\item J. Li, J-M. Guo, W.C. Shiu and A. Chang, Six classes
of trees with largest normalized algebraic connectivity,
{\it Linear Alg. Appl.}, {\bf 452}, 318-327 (2014).

\item J. Li, J-M. Guo, W.C. Shiu and A. Chang, An
edge-separating theorem on the second smallest normalized
Laplacian eigenvalue of a graph and its applications, {\it
Discrete Appl. Math.}, {\bf 171}, 104-115 (2014).

\item J. Li, J-M. Guo and W.C. Shiu, The Normalized
Laplacian Estrada Index of a Graph, {\it FILOMAT}, {\bf
28}, 365-371 (2014).

\item  Q. Wu, W.C. Shiu and P.K. Sun, Circular $L(j,k)$-labeling number of direct
product of path and cycle, {\it J. Combin. Optimization}, {\bf 27}, 355-368 (2014).

\item W.H. Chan, P.C.B. Lam and W.C. Shiu, Characterization of 3-regular Halin
graphs with edge-face total chromatic number equal to
four, {\it Ars Combin.}, {\bf 113}, 257-262 (2014).

\item J-M. Guo, W.C. Shiu and J. Li, On the Laplacian,
signless Laplacian and normalized Laplacian characteristic
polynomials of a graph, {\it Czechoslovak Mathematical
Journal}, {\bf 63}, 701-720 (2013).

\item W.C. Shiu and M.-H. Ho, Full friendly index sets and
full product-cordial index sets of some permutation
Petersen graphs, {\it J. Combin. Number Theory}, {\bf
5(3)}, 227-244 (2013).

\item W.H. Chan, R.M. Low and W.C. Shiu, Group-antimagic labelings of graphs,
{\it Congr. Numer.}, {\bf 217}, 21-31 (2013).

\item W.C. Shiu and M.-H. Ho, Full friendly index sets of slender and flat cylinder graphs,
{\it Transactions on Combinatorics}, {\bf 2(4)}, 63-80 (2013).

\item  W.C. Shiu and R.M. Low, Group-magic labelings of graphs with deleted edges,
{\it Australas. J. Combin.}, {\bf 57}, 3-19 (2013).

\item J-M. Guo, J. Li and W.C. Shiu, A note on the upper bounds for the Laplacian spectral radius of graphs,
{\it Linear Alg. Appl.}, {\bf 439}, 1657-1661 (2013).

\item W.H. Chan, W.C. Shiu, P.K. Sun and X. Zhu, The
strong game colouring number of directed graphs, {\it Discrete Math.}, {\bf 313}, 1070-1077 (2013).

\item H. Zhang, W.C. Shiu and P.K. Sun, A Relation between
Clar Covering Polynomial and Cube Polynomial, {\it
MATCH Communications in Mathematical and Computer
Chemistry}, {\bf 70}, 477-492 (2013).


\item W.C. Shiu and Q. Wu, $L(j,k)$-number of direct product of path and cycle,
{\it Acta Math Sinica}, {\bf 29}, 1437-1448 (2013).


\item W.C. Shiu, Product-cordial index set for Cartesian product of a graph with a path, {\it J. Comb. Number Theory}, {\bf 4(3)} , 177-194 (2012).

\item J. Li, J-M. Guo and W.C. Shiu, On the second largest
Laplacian eigenvalues of graphs, {\it Linear
Alg. Appl.}, {\bf 438}, 2438-2446 (2013).

\item J. Li, J-M. Guo and W.C. Shiu, On the spectral
radius of unicyclic graphs with fixed girth, {\it Ars Combin.}, {\bf 108}, 65-80 (2013).

\item W.C. Shiu and R.M. Low, The integer-magic spectra of
bicyclic graphs without pendant, {\it Congr. Numer.}, {\bf 214}, 65-73 (2012).


\item W.C. Shiu, The non-edge-magic simple connected cubic graph of
order $10$, {\it Journal of Combinatorial Mathematics
and Combinatorial Computing}, {\bf 83}, 225-241 (2012).


\item W.C. Shiu, H. Chen, X.G. Chen and P.K. Sun, On the total
restrained domination number of direct products of graphs,
{\it Discussiones Math. Graph Theory}, {\bf 32}, 629-641 (2012).

\item H. Zhou, W.C. Shiu and P.C.B. Lam, The
$L(2,1)$-choosability of cycle, {\it Transactions on
Combinatorics}, {\bf 1(3)}, 21-38 (2012).


\item  P.K. Sun and W.C. Shiu, Some Results on incidence coloring,
star arboricity and domination number, {\it Australas.
J. Combin.}, {\bf 54}, 107-114 (2012).

\item Y. Hou, Z. Tang and W.C. Shiu, Some results on graphs with exactly two main
eigenvalues, {\it Appl. Math. Lett.}, {\bf 25},
1274-1278  (2012).

\item J. Li, J-M. Guo and W.C. Shiu, The smallest values
of algebraic connectivity for trees, {\it Acta Math.
Sinica}, {\bf 28}, 2021-2032 (2012).

\item W.C. Shiu, S-M. Lee, Full friendly index sets and
full product-cordial index sets of twisted cylinders, {\it J. Combinatorics and
Number Theory}, {\bf 3(3)}, 209-216 (2012).

\item J-M. Guo, J. Li and W.C. Shiu, The smallest Laplacian spectral
radius of graphs with a given clique number, {\it
Linear Alg. Appl.}, {\bf 437}, 1109-1122 (2012).

\item D-J. Huang, W.C. Shiu and W-F. Wang, On the
vertex-arboricity of planar graphs without 7-cycles,
{\it Discrete Math.}, {\bf 312}, 2304-2315 (2012).

\item W.C. Shiu and H. Kwong, Product-cordial index and
friendly index of regular graphs, {\it Transactions on
Combinatorics}, {\bf 1(1)}, 15-20 (2012).

\item W.C. Shiu and F.S. Wong, Full friendly index sets
of cylinder graphs, {\it Australas. J. Combin.}, {\bf
52}, 141-162 (2012).

\item W.H. Chan, R.M. Low, W.C. Shiu, J.P.
Steinberger and K.Y. Wan, On a switch-setting problem
arising from a variation of the lights out game, {\it
JP J. Algebra, Number Theory Appl.}, {\bf 24}, 173-184
(2012).


\item X. Chen and W.C. Shiu, A new upper bound on global
defensive alliance number in trees, {\it Electronic J.
Combin.}, {\bf 18}, \#P202 (2011).

\item W.C. Shiu, W.H. Chan, Z.F. Zhang and L. Bian, On
the adjacent vertex-distinguishing acyclic edge
coloring of graphs, {\it Applied Math. J. Chinese
University}, {\bf 26}, 439-452 (2011).

%and {\it Journal of Systems Science and Mathematics
%Sciences} (Chinese Translation), (2012).

\item C.O. Chow and W.C. Shiu, Counting simsun
permutations by descents, {\it Annals of
Combinatorics}, {\bf 15}, 625-635 (2011).

\item W.C. Shiu, J-M. Guo and J. Li, The minimum
algebraic connectivity of caterpillar unicyclic graphs,
{\it Electronic Journal of Linear Algebra}, {\bf 22},
838-848 (2011).

\item Y. Hou, W.C. Shiu and W.H. Chan, Graphs whose critical
groups have larger rank, {\it Acta Math. Sinica}, {\bf
27}, 1663-1670, (2011).

\item W.C. Shiu, J. Li and W.H. Chan, A note on the Laplacian
Estrada index of a graph, {\it MATCH Communications in
Mathematical and Computer Chemistry}, {\bf 66}, 777-784
(2011).


\item J. Li, W.C. Shiu and W.H. Chan, On the Laplacian
Spectral Radii of Bipartite Graphs, {\it Linear Alg.
Appl.}, {\bf 435}, 2183-2192 (2011).

\item J-M. Guo, W.C. Shiu and J. Li, The
algebraic connectivity of lollipop graphs, {\it Linear
Alg. Appl.}, {\bf 434} , 2204-2210 (2011).

\item W.C. Shiu and F.S. Wong, Strong vertex-graceful
labelings for some double cycles, {\it Congr. Numer.},
{\bf 202}, 17-24 (2010).

\item J. Li, J-M. Guo and W.C. Shiu, The orderings of
bicyclic graphs and connected graphs by algebraic
connectivity, {\it Electronic Journal of
Combinatorics}, {\bf 17}, \#R162, (2010).

\item Y. Hou and W.C. Shiu, The spectrum of the edge
corona of two graphs, {\it Electronic Journal of Linear
Algebra}, {\bf 20}, 586-594 (2010).

\item W.C. Shiu, H. Zhang and S. Liu, Maximal resonance of cubic
bipartite polyhedral graphs, {\it J. Math. Chem.}, {\bf
48}, 676-686 (2010).

\item W.C. Shiu, X. Chen and W.H. Chan, Some results
on matching and total domination in graphs, {\it
Application Analysis and Discrete Math.}, {\bf 4},
241-252 (2010).

\item X. Chen and W.C. Shiu, A note on weakly connected domination number in
graphs, {\it Ars Combin.}, {\bf 97}, 193-201 (2010).

\item J. Li, W.C. Shiu and A. Chang, The Laplacian
spectral radius of graphs, {\it Czechoslovak
Mathematical Journal}, {\bf 60 (135)}, 835-847 (2010).

\item J. Li, J-M. Guo and W.C. Shiu, The smallest values
of algebraic connectivity for unicyclic graphs, {\it
Discrete Appl. Math.}, {\bf 158}, 1633-1643 (2010).

\item J. Li, W.C. Shiu, W.H. Chan and A. Chang,
Ordering trees by their largest Laplacian eigenvalues,
{\it Graph Theory Notes of New York}, {\bf LVIII}, 9-18
(2010).
\item W.C. Shiu, W. Li, W.H. Chan, On the spectral of the
fullerene admitting nontrivial cyclic-5-cutset, {\it
Australasian Journal of Combinatorics}, {\bf 47}, 41-51
(2010).

\item W.C. Shiu and M.H. Ling, Full Friendly Index Sets
of Cartesian Products of two Cycles, {\it Acta Math.
Sinica}, {\bf 26}, 1233-1244 (2010).

\item W.C. Shiu, X.G. Chen and W.H. Chan, Triangle-free
graphs with large independent domination number, {\it
Discrete Opt.}, {\bf 7}, 86-92 (2010).

\item W.C. Shiu, X. Chen and W.H. Chan, Uniformly pair-bonded
trees, {\it Ars Combin.}, {\bf 94}, 71-78 (2010).

\item J. Li, W.C. Shiu and A. Chang, The number of spanning trees
of a graph, {\it Applied Math. Letters}, {\bf 23},
286-290 (2010).

\item H. Zhang, D. Ye and W.C. Shiu, Forcing matching
number of fullerene graphs, {\it Appl. Discrete Math.},
{\bf 158}, 573-582 (2010).

\item J. Li, W.C. Shiu and A. Chang, On the $k$-th Laplacian
Eigenvalues of Trees with Perfect Matchings, {\it
Linear Algebra Appl.}, {\bf 432}, 1036-1041 (2010).

\item X. Chen and W.C. Shiu, A note on the domination
dot-critical graphs, {\it Discrete Appl. Math.}, {\bf
157}, 3743-3745 (2009).

\item W.C. Shiu, J. Li and W.H. Chan, Unicyclic
and bicyclic graphs of rank 4 or 5, {\it Congr.
Numer.}, {\bf 198}, 51-62 (2009).

\item W.C. Shiu and F.S. Wong, Extreme Friendly
Indices of $C_m\times P_n$, {\it Congr. Numer.}, {\bf
197}, 65-75 (2009).

\item W.H. Chan, P.C.B. Lam and W.C. Shiu, Edge-face
total chromatic number of Halin graphs, {\it SIAM J.
Discrete Math.} {\bf 23}, 1646-1654 (2009).

\item P.C.B. Lam,  T.M. Wang, W.C. Shiu and G. Gu, On
Distance Two Labelling of Unit Interval Graphs, {\it
Taiwanese J. Math.}, {\bf 13(4)}, 1167-1179 (2009).

\item W.C. Shiu and R.M. Low, $\mathbb Z_k$-magic labelings of fans and
wheels with magic-value zero, {\it Australas. J.
Combin.}, {\bf 45}, 309-316 (2009).

\item W.C. Shiu and H. Kwong, An algebraic approach for finding
balance index sets, {\it Australas. J. Combin.}, {\bf
45}, 139-155 (2009).

\item J. Li, W.C. Shiu, W.H. Chan and A. Chang, On the spectral
radius of graphs with connectivity at most $k$, {\it J. Math.
Chem.}, {\bf 46}, 340-346 (2009).

\item W.C. Shiu and L.Z. Zhang, The maximum Randi\'c index of
chemical trees with $k$ pendants, {\it Discrete Math.}, {\bf
309}, 4409-4416 (2009).

\item J. Li, W.C. Shiu and W.H. Chan,
The Laplacian spectral radius of some graphs, {\it Linear Alg.
Appl.}, {\bf 431}, 99-103 (2009).

\item Z.H. Chen,  P.C.B. Lam and W.C. Shiu, Collapsible graphs and reduction of
line graphs, {\it Discrete Math.}, {\bf 309}, 3173-3184
(2009).

\item J. Li, W.C. Shiu and A. Chang, On the Laplacian Estrada index of a
graph, {\it Application Analysis and Discrete Math.},
{\bf 3}, 147-156 (2009).

\item W.C. Shiu and W.K. Tam, The strong chromatic index of
complete cubic Halin graphs, {\it Applied Math.
Letter}, {\bf 22}, 754-758 (2009).

\item J. Li, W.C. Shiu and W.H. Chan, Some results on the
Laplacian eigenvalues of unicyclic graphs, {\it Linear
Alg. Appl.}, {\bf 430}, 2080-2093 (2009). Erratum: From
the Editor-in Chief, {\it Linear Alg. Appl.}, {\bf
434}, xviii-xix (2011).

\item R.M. Low and W.C. Shiu, On the integer-magic spectra of graphs,
{\it Congressus Numerantium}, {\bf 191}, 193-203 (2008).

\item W.C. Shiu and M.C. Chiu, Invariant factors of Cartesian product of graphs and one
point unions of graphs, {\it Congressus Numerantium},
{\bf 191}, 173-184 (2008).

\item P. You, W.C. Shiu, W.H. Chan and A. Chang, Interchanging graph
associated with sorting by transpositions, {\it Congressus
Numerantium}, {\bf 191}, 25-31 (2008).

\item Z. Cao, C.I. Chu and W.C. Shiu, The exponential Diophantine equation
$AX^2+BY^2=\lambda k^Z$ and its applications, {\it
Taiwanese J. Math.}, {\bf 15}, 1015-1034 (2008).

\item W.C. Shiu and P.K. Sun, Invalid proofs on incidence coloring,
{\it Discrete Math.}, {\bf 308}, 6575-6580 (2008).

\item W.C. Shiu, M.H. Ling and R.M. Low, The edge-graceful spectra of connected
bicyclic graphs without pendant, {\it Journal of Combinatorial
Mathematics and Combinatorial Computing}, {\bf 66}, 171-185 (2008).

\item K.K. Poon and W.C. Shiu, On the Dirichlet's box principle,
{\it International Journal of Mathematical Education in
Science and Technology}, {\bf 39}, 833-838 (2008).

\item W.C. Shiu, Extremal Hosoya index and Merrifield-Simmons index of
hexagonal spiders, {\it Discrete Appl. Math.}, {\bf
156}, 2978-2985 (2008).

\item H. Zhang, P.C.B. Lam and W.C. Shiu, Resonance graphs and a binary coding
for the 1-factors of benzenoid systems, {\it SIAM J. Discrete Math.}, {\bf
22}, 971-984 (2008).

\item W.C. Shiu, Z. Shao, K.K. Poon and D. Zhang, A new approach to the
$L(2,1)$-labeling of some product of graphs, {\it IEEE
Trans. Circuit and Systems II}, {\bf 55}, 802-805 (2008).

\item X. Chen, W.C. Shiu and W.H. Chan, Upper bounds on paired-domination
number, {\it Appl. Math. Letters}, {\bf 21}, 1194-1198 (2008).

\item Z. Shao, R.K. Yeh, K.K. Poon and W.C. Shiu, The $L(2,1)$-labeling of
$K_{1,n}$-free graphs and its applications, {\it Applied
Math. Letters}, {\bf 21}, 1188-1193 (2008).

\item Z. Shao, S. Klavar, W.C. Shiu and D. Zhang, Improved bounds on the
$L(2,1)$-number of direct and strong products of graphs, {\it IEEE
Trans. on Circuits and System II}, {\bf 55}, 685-689 (2008).

\item W.C. Shiu and G. Liu, $k$-factors in regular graphs, {\it Acta Math. Sinica}, {\bf 24}, 1213-1220 (2008).

\item X. Chen, W.C. Shiu and H. Chen, Trees with equal total domination and
total restrained domination numbers, {\it Discussiones
Mathematicae Graph Theory}, {\bf 28}, 59-66 (2008).


\item W.C. Shiu and Harris Kwong, Full friendly index sets of $P_2\times P_n$,
{\it Discrete Math.}, {\bf 308}, 3688-3693 (2008).

\item J. Li, A. Chang and W.C. Shiu, On the nullity of bicyclic graphs,
{\it MATCH Communications in Mathematical and Computer
Chemistry}, {\bf 60}, 21-36 (2008).

\item W.C. Shiu and R.M. Low, Ring-magic labelings of graphs,  {\it
Australas. J. of Combin.}, {\bf 41}, 147-158 (2008).

\item W.H. Chan, P.C.B. Lam and W.C. Shiu,
Cyclic bandwidth with an edge added, {\it Discrete
Applied Math.}, {\bf 156}, 131-137 (2008).


\item W.C. Shiu and L.Z. Zhang, Pancyclism of $3$-domination-critical graphs
with small minimum degree, {\it Utilitas Mathematica},
{\bf 75}, 175-192 (2008).

\item W.C. Shiu and H. Zhang, A complete characterization for $k$-resonant
Klein-bottle polyhexes, {\it J. Math. Chem.}, {\bf 43}, 45-59 (2008).

\item A. Chang and W.C. Shiu, On the $k$-th eigenvalues of trees with perfect matchings,
{\it Discrete Math. and Theoretical Comp. Sci.}, {\bf 9} 321-332 (2007).

\item W.C. Shiu and M.H. Ling, Extreme friendly indices of $C_m\times C_n$,
{\it Congressus Numerantium}, {\bf 188}, 175-182 (2007).

\item W.C. Shiu, Edge-magic labeling matrices of the composition of paths with
null graphs, {\it Congressus Numerantium}, {\bf 187},
55-69 (2007).

\item W.C. Shiu and R.W. Low, Integer-magic spectra of sun graphs,
{\it J. Comb. Optimization}, {\bf 14}, 309-321 (2007).

\item Z.H. Chen, H.J. Lai, W.C. Shiu and D Li,
An $s$-Hamiltonian line graph problem, {\it Graphs and Combin.}, {\bf 23},
241-248 (2007).

\item X. Dong, W.C. Shiu, C.I. Chu and Z. Cao, The simultaneous Pell equation
$y^2-Dz^2=1$ and $x^2-2Dz^2=1$, {\it Acta Arith.}, {\bf 162}, 115-123 (2007).

\item W. Lin, P.C.B. Lam, and W.C. Shiu, Circular chromatic numbers of the
generalized Mycielskians of cycles, {\it J. of Nanjing University Mathematical
Biquarterly}, {\bf 23}, 232-241 (2006).

\item W.C. Shiu and C.I. Chu, Frequency of Fibonacci numbers in modulo $3^k$
that are congruent to $8\pmod{27}$, {\it Int. J. of Pure and Appl. Math.}, {\bf
33}, 7-21 (2006).

\item W.C. Shiu and C.I. Chu, The number of increasing nonconsecutive subpaths
in a path, {\it Graph Theory Notes of New York}, {\bf LI}, 47-49 (2006).

\item W.C. Shiu, M.H. Ling and R.M. Low, The entire edge-graceful spectra of
cycles with one chord, {\it Congressus Numerantium}, {\bf 183}, 213-219 (2006).

\item P.C.B. Lam, W.C. Shiu and G. Gu, Graphs with convex labelings,
{\it Congressus Numerantium}, {\bf 183}, 33-50 (2006).

\item W.C. Shiu, P.C.B. Lam and P.K. Sun, Cubic graphs with different incidence
chromatic numbers, {\it Congressus Numerantium}, {\bf 182}, 33-40 (2006).


\item W.C. Shiu, Super-edge-graceful labelings of some cubic graphs,
{\it Acta Math. Sinica}, {\bf 22(6)}, 1621-1628 (2006).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0410.pdf}{PDF0410}

\item W.C. Shiu and R.M. Low, Group magicness of complete $N$-partite graph,
{\it Journal of Combinatorial Mathematics and Combinatorial Computing}, {\bf
58}, 129-134 (2006).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0481.pdf}{PDF0481}

\item W.C. Shiu, P.C.B. Lam and W.K. Tam, On strong chromatic index of Halin
graph, {\it Journal of Combinatorial Mathematics and
Combinatorial Computing}, {\bf 57}, 211-222 (2006).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0323.pdf}{PDF0323}

\item A. Chen, A. Chang and W.C. Shiu, Energy ordering of unicycle graphs, {\it MATCH Commum. Math. Comput.
Chem.}, {\bf 55}, 95-102 (2006).

\item W.C. Shiu and P.C.B. Lam, Super-edge-graceful labelings of multi-level wheel graphs, fan graphs and actinia
graphs, {\it Congressus Numerantium}, {\bf 174}, 49-63 (2005).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/supgracewheel.pdf}{PDF0540}


\item W.C. Shiu, P.C.B. Lam and H. Zhang, $k$-resonance in toroidal polyhexes,
{\it J. Math. Chem.}, {\bf 38}, 451-466 (2005).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p04K0MathChemv1.pdf}{PDF04K0}

\item W.C. Shiu, A software for editing mathematics in Chinese -- PUTeX, {\it
Datum}, {\bf 42}, 29-31 (2005).

\item K.K. Poon, K.W. Yeung and W.C. Shiu, On the decimal numbers base $n$,
{\it Inter. J. Math. Edu. in Sci. and Tech.}, {\bf 36}, 601-605 (2005).

\item W.C. Shiu and C.I. Chu, Distribution of the Fibonacci number
modulo $3^k$, {\it The Fibonacci Quarterly}, {\bf 43},
22-28 (2005).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0130rev.pdf}{PDF0130}

\item P.C.B. Lam, W.C. Shiu and Z.M. Song, The 3-choosability of
plane graphs of girth 4, {\it Discrete Math.}, {\bf
294}, 297-301 (2005).

\item W.C. Shiu,  P.C.B. Lam and P.K. Sun, Construction of group-magic graphs and
some $A$-magic graphs with $A$ of even order, {\it Congressus
Numerantium}, {\bf 167}, 97-107 (2004).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/t0432.pdf}{PDF0432}



\item W.C. Shiu, Invariant factors of graphs associated with
hyperplane arrangements, {\it Discrete Math.}, {\bf
288}, 135-148 (2004).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9810shorted.pdf}{PDF9810}

\item K.K. Poon and W.C. Shiu, Sperner Lemma and its applications, {\it
Mathmedia}, {\bf 27(4)}, 42-49 (2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/Sperner.pdf}{PDF025C}

\item H. Zhang, P.C.B. Lam and W.C. Shiu, Cell rotation graphs of strongly
connected orientations of plane graphs with application, {\it Discrete Appl.
Math.}, {\bf 130}, 469-485 (2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0260final.pdf}{PDF0260}


\item D. Kremer and W.C. Shiu, Finite transition matrices for permutations
avoiding pairs of length four patterns, {\it Discrete Math.}, {\bf 268},
171-183 (2003).

\item P.C.B. Lam, W.C. Shiu and H. Zhang, Elementary block of plane bipartite
graphs, {\it MATCH Communications in Mathematical and
Computer Chemistry}, {\bf 49}, 127-137 (2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/Zhangh.pdf}{PDF0240}

\item W.C. Shiu, P.C.B. Lam and L.Z. Zhang, Fully angular hexagonal chains
extremal with regard to the largest eigenvalue, {\it
Indian J. of Chemistry}, {\bf 42A}, 1298-1303 (June,
2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0281sub.pdf}{PDF0281}

\item W.C. Shiu, P.C.B. Lam and Y. Li, On some three-color Ramsey numbers,
{\it Graphs and Combinatorics}, {\bf 19}, 249-258 (2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/gc1373.pdf}{PDF9925}

\item W.C. Shiu, P.C.B. Lam and L.Z. Zhang, Extremal $k^*$-cycle
resonant hexagonal chains, {\it J. Math. Chem.}, {\bf
33}, 17-28 (2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0150final.pdf}{PDF0150}


\item W.C. Shiu, P.C.B. Lam and H. Zhang, Clar and sextet
polynomials of buckminsterfullerene, {\it J. Molecular
Structure: THEOCHEM}, {\bf 622}, 239-248 (2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0210Theochem4.pdf}{PDF0210}

\item W.C. Shiu and P.C.B. Lam, More on the generalized Fibonacci numbers and
associated bipartite graphs, {\it International
Mathematics Journal}, {\bf 3(1)}, 5-9 (2003).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0101inter.pdf}{PDF0101}

\item W.C. Shiu, P.C.B. Lam and Y. Li, On generalized Ramsey
numbers, {\it Discrete Math.}, {\bf 258}, 383-388
(2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0020fin.pdf}{PDF0020}


\item W.C. Shiu, P.C.B. Lam, F. Zhang and H. Zhang, Normal
components, Kekul\'e patterns, and Clar patterns in plane bipartite graph, {\it
Journal of Mathematical Chemistry}, {\bf 31(4)}, 405-420 (2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0230.pdf}{PDF0230}


\item W.C. Shiu, P.C.B. Lam and S-M. Lee, On a construction of
supermagic graphs, {\it Journal of Combinatorial
Mathematics and Combinatorial Computing}, {\bf 42},
147-160 (2002).
(\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0040pub.pdf}{PDF0040})

\item W.C. Shiu, P.C.B. Lam and S-M Lee, Edge-magic indices of
$(n, n-1)$-graphs, {\it Electronic Notes in Discrete Mathematics}, {\bf 11}
(July, 2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9815updated.pdf}{PDF9815}

\item W.C. Shiu, P.C.B. Lam and H.L. Cheng, Edge-gracefulness of
the composition paths with null graphs, {\it Discrete
Math.}, {\bf 253}, 63-76 (2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0015fin.pdf}{PDF0015}

\item W.C. Shiu, P.C.B. Lam and D.L. Chen, On incidence coloring for some cubic
graphs, {\it Discrete Math.}, {\bf 252}, 259-266 (2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0055corr.pdf}{PDF0055}

\item W.C. Shiu, P.C.B. Lam and K.K. Poon, On Wiener numbers of
polygonal nets, {\it Discrete Applied Math.}, {\bf
122}, 251-261 (2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0060fin.pdf}{PDF0060}

\item W.C. Shiu and S-M. Lee, Some edge-magic cubic graphs, {\it Journal of
Combinatorial Mathematics and Combinatorial Computing}, {\bf 40}, 115-127
(2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9825.pdf}{PDF9825}

\item P.C.B. Lam, W.C. Shiu and W.H. Chan, Characterization of
graphs with equal bandwidth and cyclic bandwidth, {\it
Discrete Math.}, {\bf 242}, 283-289 (2002).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9919fin.pdf}{PDF9919}


\item W.C. Shiu, P.C.B. Lam, D-L. Chen and L-Y. Miao, On the
$\ell$-distance face coloring of regular plane graphs,
{\it Congressus Numerantium}, {\bf 152}, 85-88  (2001).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0105sub.pdf}{PDF0105}


\item  P.C.B. Lam, J. Liu, W.C. Shiu and Z.M. Song, A class of
graph with $\chi^*$ close to $\chi -1$, {\it Congressus
Numerantium}, {\bf 150}, 65-68 (2001).


\item P.C.B. Lam, W.C. Shiu, C.S. Tong and Z.F. Zhang, On the
equitable chromatic number of complete $n$-partite
graphs, {\it Discrete Applied Math.}, {\bf 113},
307-310 (2001).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9605.pdf}{PDF9605}

\item W.C. Shiu, S-M. Lee and K. Schaffer, Some $k$-fold
edge-graceful labelings of $(p, p-1)$-graphs, {\it
Journal of Combinatorial Mathematics and Combinatorial
Computing}, {\bf 38}, 81-95 (2001).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9830.pdf}{PDF9830}

\item P.C.B. Lam, W.C. Shiu and B. Xu, On structure of some plane
graphs with application to choosability, {\it J. Comb.
Theory, Ser. B}, {\bf 82}, 285-296 (2001).

\item P.C.B. Lam, W.C. Shiu, F. Sun, J.F. Wang and G. Yan, Linear vertex
arboricity, independence number and clique cover number, {\it Ars Combin.}, {\bf 58}, 121-128
(2001). \href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9710.pdf}{PDF9710}

\item W.C. Shiu, P.C.B. Lam and H.L. Cheng, Supermagic labeling of an
$s$-duplicate of  $K_{n,n}$, {\it Congressus Numerantium}, {\bf 146}, 119-124
(2000).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0010.pdf}{PDF0010}

\item P.C.B. Lam, W.C. Shiu and W.H. Chan, Edge-face total chromatic number of
3-regular Halin graph, {\it Congressus Numerantium},
{\bf 145}, 161-165 (2000).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p0030.pdf}{PDF0030}

\item M.H.F. Chu and W.C. Shiu, Theoretical studies of AlGaAs-GaAs
multiple-quantum-well single channel waveguide defined
by ion-implantation-induced intermixing, {\it
Proceedings of SPIE}, {\bf 3944}, 149-163 (2000).

\item B.L. Weiss, Y. Chan, W.C. Shiu and E.H. Li, The electro-optic properties
of interdiffused InGaAs/InP quantum well structures,
{\it J. of Appl. Phys.}, {\bf 88 (6)}, 3418-3425
(2000).

\item P.C.B Lam, G. Liu, G. Li and W.C. Shiu, Orthogonal $(g,f)$-factorization
in networks, {\it Network}, {\bf 35 (4)}, 274-278
(2000).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9917.pdf}{PDF9917}

\item P.C.B. Lam, W.C. Shiu and H.L. Cheng, Knight's tour on hexagonal nets,
{\it Congressus Numerantium}, {\bf 141}, 73-82 (1999).

\item W.C. Shiu, P.C.B.
Lam and S-M Lee, Edge-magic index set of
$(p,p)$-graphs, {\it Congressus Numerantium}, {\bf
137}, 97-107 (1999).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9901.pdf}{PDF9901}

\item P.C.B. Lam, J. Liu, W.C. Shiu and J. Wu, Some sufficient conditions for a
planar graph to be class 1, {\it Congressus
Numerantium}, {\bf 136}, 201-205 (1999).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9904.pdf}{PDF9904}

\item P.C.B. Lam,
W.C. Shiu and B. Xu, Edge game coloring of graphs, {\it
Graph Theory Notes of New York}, {\bf XXXVII:3}, 17-19
(1999).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9807.pdf}{PDF9807}

\item K.F. Fang, W.C. Shiu and J.X. Pan, Uniform designs based on Latin
squares, {\it Statistica Sinica}, {\bf 9}, No. {\bf 3},
905-912 (1999).


\item P.C.B. Lam, W.C. Shiu and L. Sun, On independent domination number of
regular graphs, {\it Discrete Math.}, {\bf 202},
135-144 (1999).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9702.pdf}{PDF9702}

\item W.C. Shiu, P.C.B. Lam and Z. Zhang, Entire chromatic number of
maximal outerplanar graphs with maximum degree at most
$4$, {\it Proc. 8th Quadrennial Internat. Conf. on
Graph Theory, Combin., Algor. and Appl.}, Vol. {\bf
II}, 591-595 (1999).

\item W.C. Shiu, P.C.B. Lam and S-M. Lee, Edge-magicness of the composition of
a cycle with a null graph, {\it Congressus Numerantium}, {\bf 132}, 9-18
(1998).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9703.pdf}{PDF9703}


\item J. Micallef, A. Brincat and W.C. Shiu, Effects of interdiffusion-induces
strain in Ga$_{0.51}$In$_{0.49}$P---GaAs intermixed
quantum wells, {\it IEEE Journal of Selected Topics in
Quantum Electronics}, {\bf 4} No. {\bf 4}, 675-684
(1998).

\item J. Micallef. A. Brincat and W.C. Shiu, Cation interdiffusion in
GaInP/GaAs single quantum wells, {\it Materials
Research Society Symp. Proceeding}, {\bf 484}, 441-446
(1998).

\item W.C. Shiu and P.C.B. Lam, Wiener numbers of some pericondensed benzenoid
molecule systems, {\it Congressus Numerantium}, {\bf
126}, 113-124 (1997).

\item P.C.B. Lam, W.C. Shiu and Y.X. Lam, Duality in the bandwidth problem,
{\it Congressus Numerantium}, {\bf 124}, 117-127 (1997).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/duality.pdf}{PDF9520}


\item W.C. Shiu, P.C.B. Lam and I. Gutman, Wiener number if hexagonal
bitrapeziums and trapeziums, {\it Bull. Acad. Serbe
Sci. Arts (Cl. Sci. Math. Natur.)}, {\bf 114}, 9-25
(1997).

\item P.C.B. Lam, W.C. Shiu and W.H. Chan, On bandwidth and cyclic bandwidth of
graphs, {\it Ars Combin.}, {\bf 47}, 147-152 (1997).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9610.pdf}{PDF9610}

\item W.C. Shiu and Y.P. Tang, Existence of ideal matrices, {\it Ars
Combin.}, {\bf 47}, 87-92 (1997).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/ideal.pdf}{PDF9620}

\item W.C. Shiu, Decoding de Bruijn arrays constructed by FFMS method, {\it Ars
Combin.}, {\bf 47}, 33-48 (1997).

\item W.C. Shiu, C.S. Tong and P.C.B. Lam, Wiener number of hexagonal
jagged-rectangles, {\it Discrete Appl. Math.}, {\bf
80}, 83-96 (1997).

\item P.C.B. Lam, W.C. Shiu, W.H. Chan and Y.X. Lin, On the bandwidth of convex
triangulation meshes, {\it Discrete Math.}, {\bf 173},
285-289 (1997).

\item W.C. Shiu and P.C.B. Lam, The Wiener number of hexagonal net, {\it
Discrete Appl. Math.}, {\bf 73}, 101-111 (1997).


\item Y. Chan, W.C. Shiu, W.K. Tsui and E.H. Li, Multiple cations
interdiffusion in
In$_{0.53}$Ga$_{0.47}$As/In$_{0.52}$Al$_{0.48}$As
quantum well, {\it Materials Research Society Symp.
Preceeding}, {\bf 450}, 377-382 (1997).

\item J. Micallef, J.L. Borg and W.C. Shiu, Polarization insensitivity in
interdiffused, strained  InGaAs/InP quantum wells, {\it Materials Research Society Symp.
Proceeding}, {\bf 450}, 371-376 (1997).

\item W.C. Shiu, C.S. Tong and P.C.B. Lam, Wiener number of some polycyclic
graphs, {\it Graph Theory Notes of New York}, {\bf
XXXII:2}, 10-15 (1997).

\item I. Gutman, G. D\"om\"ot\"or, P.C.B. Lam, W.C. Shiu and L. Popvoi\'{c},
Szeged indices of benzenoid hydrocarbons, {\it
Polycyclic Aromatic Compounds}, {\bf 8}, 259-270
(1996).

\item W.K. Tsui, E.H. Li, W.C. Shiu and Y. Chan, Three species interdiffusion
and their effect on the variation of strains in
In$_{0.53}$Ga$_{0.47}$As/In$_{0.52}$Al$_{0.48}$As QW,
{\it Third Chinese Optoelectronics Workshop},
Changchun, 266-267 (1996).

\item W.C. Shiu, P.C. Lam and I. Gutman, Wiener number of hexagonal
parallelograms, {\it Graph Theory Notes of New York},
{\bf XXX:6}, 21-25 (1996).

\item W.C. Shiu, Difference sets in groups containing subgroups of index 2,
{\it Ars Combin.}, {\bf 42}, 199-205 (1996).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/p9510.pdf}{PDF9510}

\item E.H. Li, J. Micallef and W.C. Shiu, The optical properties of
InGaAs(P)/InP under group V sublattice two-phase interdiffusion, {\it Materials Research
Society Symp. Proceeding}, {\bf 417}, 289-293 (1996).

\item W.C. Shiu, S.L. Ma and K.T. Fang, On the rank of cyclic Latin squares,
{\it Linear and Multilinear Algebra}, {\bf 40}, 183-188 (1995).

\item W.C. Shiu, Correction to algebraic structure of Schur rings, {\it Chinese
Journal of Mathematics (R.O.C.)}, {\bf 23}, 193-194 (1995).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/Shiu1995.pdf}{PDF1995}

\item W.C. Shiu, J. Micallef, I. Ng, and E.H. Li, Effects of
different cation and anion interdiffusion rates in
disordered In$_{0.53}$Ga$_{0.47}$As/InP single quantum
wells, {\it Japanese Journal of Applied Physics}, {\bf
34}, {\bf part 1}, No. {\bf 4A}, 1778-1783 (1995).

\item W.C. Shiu, Algebraic structure of Schur rings, {\it Chinese Journal of
Mathematics (R.O.C.)}, {\bf 21}, 55-71 (1993).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/Shiu1993correction.pdf}{PDF1993}

\item W.C. Shiu, Schur rings over dihedral groups, {\it Chinese Journal of
Mathematics (R.O.C.)}, {\bf 18}, 209-223 (1990).
\href{http://www.math.hkbu.edu.hk/\~wcshiu/PDF/Shiu1990.pdf}{PDF1990}
\end{enumerate}

\end{document}
